---
title: "Homework 4"
author: "Zehao Wang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(tidyverse)
library(MASS)
```

## 1. In a study for shortleaf pines, the diameter (x, in inches) and volume (y, in cubic feet) of the pines were collected. The investigators wanted to build a regression model between the two variables. Use appropriate tools/approaches to answer the following questions: 

```{r}
data <- read_table("HW4_data.txt")
```

## 1.1 Fit a simple regression model and visually inspect the data/results to see whether there is evidence for potential issues. 

```{r}
lm1 <- lm(Vol ~ Diam, data)
summary(lm1)
```

```{r fig.height=3, fig.width=4}
data1 <- tibble(x = data$Diam,
                 y_t = data$Vol,
                 y_p = lm1$fitted.values)
ggplot(data1) +
    geom_point(mapping = aes(x, y_t, color = "True values")) +
    geom_line(mapping = aes(x, y_p, color = "Predict values")) +
    theme_bw() +
    xlab("Diam") +
    ylab("Vol")
```

```{r fig.height=2.5, fig.width=3.5}
plot(lm1)
```

From these plot, we could see that the residuals V.S. fitted values shows the relationship between them may be quadratic. And the scale-location plot shows that the different sample points may have different variance. And the Leverage plot shows that there are some influential points. 




## 1.2 Conduct a Box-Cox transformation for the volume. Visually inspect the data/results to see whether there is evidence for potential issues. 

```{r fig.height=3, fig.width=4}
bc <- boxcox(data$Vol ~ data$Diam)
(lambda <- bc$x[which.max(bc$y)])
```

```{r}
data2 <-
    tibble(x = data$Diam,
           Vol = (data$Vol ^ lambda - 1) / lambda)

lm2 <- lm(Vol ~ x, data2)

summary(lm2)

data2 <- tibble(data2, y_p = lm2$fitted.values)
```

```{r fig.height=3, fig.width=4}
ggplot(data2) +
    geom_point(mapping = aes(x, Vol, color = "True values")) +
    geom_line(mapping = aes(x, y_p, color = "Predict values")) +
    theme_bw() +
    xlab("Diam") +
    ylab("Vol")
```

```{r fig.height=2.5, fig.width=3.5}
plot(lm2)
```

These plots suggest there is no issue in the model with Box-Cox transformation. 



## 1.3 Conduct a log-transformation for diameter alone. Visually inspect the data/results to see whether there is evidence for potential issues. 

```{r}
data3 <- tibble(x = log(data$Diam), Vol = data$Vol)

lm3 <- lm(Vol ~ x, data3)

summary(lm3)

data3 <- tibble(data3, y_p=lm3$fitted.values)
```

```{r fig.height=3, fig.width=4}
ggplot(data3) +
    geom_point(mapping = aes(x, Vol, color = "True values")) +
    geom_line(mapping = aes(x, y_p, color = "Predict values")) +
    theme_bw() +
    xlab("Diam") +
    ylab("Vol")
```

```{r fig.height=2.5, fig.width=3.5}
plot(lm3)
```

The model with log transformation for $X$ is worse than the above two. So, it is not appropriate to have log transformation for $X$. 



## 1.4 Conduct transformation on both volume and diameter. Inspect the data/results and compare them with results from a-c to see whether fitting has been improved. 

```{r}
data4 <- tibble(x=log(data$Diam), Vol=data2$Vol)

lm4 <- lm(Vol~x, data4)

summary(lm4)
```

```{r}
data4 <- tibble(data4, y_p=lm4$fitted.values)
```

```{r fig.height=3, fig.width=4}
ggplot(data4) +
    geom_point(mapping = aes(x, Vol, color = "True values")) +
    geom_line(mapping = aes(x, y_p, color = "Predict values")) +
    theme_bw() +
    xlab("Diam") +
    ylab("Vol")
```



```{r fig.height=2.5, fig.width=3.5}
plot(lm4)
```

The fitting result in (b) is best among the four models. 


