---
title: "Regression Analysis Homework 3"
author: "Zehao Wang"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

Environment Information. 

```{r warning=FALSE}
sessionInfo()
```


## 1. 
In a crime rate study, several variables have been measured (see data in the attached file “HW3_data.txt”), including: 

- Year: "Year"
- fertil: "Fertility Rate per 1000"
- labor: "Labor Force Participation Rate per 1000"
- postsec:  "Post Secondary Degree Rate per 1000"
- findict:  "Female Indictable-Offense Conviction Rate per 100,000"
- ftheft:  "Female Theft Conviction Rate per 100,000"
- mindict:  "Male Indictable-Offense Conviction Rate per 100,000"
- mtheft: "Male Theft Conviction Rate per 100,000"

The investigators were interested in “ftheft” (Y), and effects by the other factors (X’s) including fertile, labor, postsec, and mtheft. Linear regression analysis is conducted. 

### A. Based on the bivariate plots between ftheft and a particular predictor, indicate the potential relationships between ftheft and the predictors. 

```{r message=FALSE, warning=FALSE}
data <- read_table("HW3_data.txt")
```

```{r fig.height=3, fig.width=4}
data %>%
    ggplot(mapping = aes(fertil, ftheft)) +
    geom_point() +
    theme_bw()

data %>%
    ggplot(mapping = aes(labor, ftheft)) +
    geom_point() +
    theme_bw()

data %>%
    ggplot(mapping = aes(postsec, ftheft)) +
    geom_point() +
    theme_bw()

data %>%
    ggplot(mapping = aes(mtheft, ftheft)) +
    geom_point() +
    theme_bw()
```

From these plots, `labor` and `postsec` have a positive linear relationship with `ftheft`. And other two variables seem to have no linear relationship with `ftheft`. 

### B. When all four X factors are in the model, create the plot between residuals and “year”. Any hints for violation of regression assumptions?

```{r}
lm_1 <- lm(ftheft ~ fertil + labor + postsec + mtheft, data)
```

```{r}
plot(lm_1)
```


```{r fig.height=3, fig.width=4}
tibble(x = data$year, y = lm_1$residuals) %>%
    ggplot(mapping = aes(x, y)) +
    geom_point() +
    theme_bw()
```

The distribution of the residuals appears to be random, so that no violation of the assumptions can be seen. 

### C. Conduct influence analysis for the data set. Any outliers/influence points? Explain. 







