\documentclass[12pt]{article}

\usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry}

% \linespread{1.5}

\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\usepackage{amsfonts} 
\usepackage{amsmath}
\usepackage{newtxtext}
% \usepackage{ulem}
\usepackage{amssymb}
\usepackage[backend=biber]{biblatex}
\addbibresource{my.bib}
\usepackage{newtxmath}
\usepackage{hyperref}

\linespread{1.3}
\setlength{\parskip}{3mm}
\setlength{\parindent}{2em}


\newenvironment{exercise}[1]{\begin{tcolorbox}[colback=black!15, colframe=black!80, breakable, title=#1]}{\end{tcolorbox}}

\newenvironment{proof}{\begin{tcolorbox}[colback=white, colframe=black!50, breakable, title=Proof. ]\setlength{\parskip}{0.8em}}{\,\\\rightline{$\square$}\end{tcolorbox}}

\newenvironment{solution}{\begin{tcolorbox}[colback=white, colframe=black!50, breakable, title=Solution. ]\setlength{\parskip}{0.8em}}{\end{tcolorbox}}

\newcommand{\pder}{\partial\,}

\newcommand{\der}{\,\mathbf{d}}

\title{\textsc{Analysis: Homework 3}}
\author{\textsc{Zehao Wang}}
\date{\today}

% \vspace{-30pt}

\begin{document}
    \maketitle

    \begin{exercise}{1}
        Let $X$ be a finite set with $n$ elements. Find the number of $\sigma$-algebras in $X$. Give a combinatorial description of this problem. 
    \end{exercise}

    \begin{solution}
        For a $n$-element set $X$, its $\sigma$-algebra can be generated from partitions of $X$. So, we need to know the number of different ways to partition the set $X$. And the number of different ways to partition a set is called \emph{Bell Number}\footfullcite{bellnumber}. Bell number of $n$-element set $X$ is denoted $B_n$. For an example, if $X=\{a,b,c\}$, then $B_3=5$. Because
        \[\{(a), (b,c)\},\qquad\{(b), (a,c)\},\qquad\{(c), (a,b)\}, \qquad\{(a,b,c)\},\qquad\{(a), (b), (c)\}\]
        And the union of any above set with $\{\varnothing, X\}$ would be a $\sigma$-algebra. 
        Hence, the number of $\sigma$-algebras in $n$-element set $X$ is $B_n$, which can be calculate by $B_n=\sum_{i=0}^{n-1}B_i\binom{n-1}{k}$. 
    \end{solution}

    \begin{exercise}{2}
        Let $E\in\mathbb{R}$ be a measurable set. Prove that 
        \[E=\left(\bigcup_{k=1}^\infty F_k\right)\cup G\]
        where each $F_k$ is compact, and $\mu(G)=0$. Here $\mu$ is Lebesgue measure. 
    \end{exercise}

    \begin{proof}
        If $E$ is Lebesgue measurable, for any $\varepsilon>0$, there exists a set $N$, such that
        \[
            \mu(E-N)<\varepsilon, 
        \]
        Let $B_n$ be a closed ball with radius $n$ and center at point $0$. So, $F_k=N\cap B_k$ is closed, and it is compact. And $F_k\uparrow N$, $E-F_k\downarrow E-N$. Hence, for a large $N$, if $k>N$, then $\mu(E-F_k)<\varepsilon$. In this case, let $G=E-\bigcup_{k=1}^nF_k=E-N$, $\mu(G)=0$. 
    \end{proof}

    \begin{exercise}{3}
        Suppose $f$ is a measurable function defined on $E\subset\mathbb{R}$ with $\mu(E) < \infty$ and suppose $f$ is finite except on a subset $F \subset E$ with $\mu(F) = 0$. Show that for any $\varepsilon > 0$, there exists a bounded function $g$, defined on $E$, such that
        \[
            \mu(\{x\in E:|f(x)-g(x)|>0\})<\varepsilon. 
        \]
    \end{exercise}

    \begin{proof}
        $f$ is measurable, for $\{-\infty, -n\}\cup\{n,\infty\}\in\mathbb{R}$, define 
        \[A_n=f^{-1}(\{-\infty, -n\}\cup\{n,\infty\})\in E. \] 
        We can know $A_1\supset A_2\supset A_3\supset\cdots$. Because $\mu(E)<\infty$, $\mu(A_1)<\infty$. So, for any $n\in\mathbb{N}$, $E-A_n$ is bounded, and in this case, let $g=f$. 

        For the set $A_n$, $f$ is not bounded, but $\lim_{n\to\infty}\cap_nA_n$ is actually the empty set. So, \[\lim_{n\to\infty}\mu(\cap_nA_n)=0. \]
        Let $A=\lim_{n\to\infty}\cap_nA_n$, $\mu(A)=0$. So, for any $\varepsilon>0$, $\mu(\{x\in A:|f(x)-g(x)|>0\})=0<\varepsilon$. 

        Got some hints from this website\footfullcite{2304794}. 
    \end{proof}

    \begin{exercise}{4}
        Let $(X; \mathscr{S}; \mu)$ be a measure space and $f : (X; \mathscr{S}) \to (Y; \mathscr{T} )$ be a measurable function (define what this is). Define a function on subsets of $Y$ by using a reasonable rule (Think about how you would bring the measure from $X$ to $Y$. This process is called the measure induced by $f$). Discuss the relation of this problem with the notion of the distribution of a random variable. 
    \end{exercise}

    \begin{solution}
        We want to transfer the measure $\mu$ on measurable space $(X,\mathscr{S})$ to another measurable space $(Y,\mathscr{T})$ by using a measurable function $f$. Assume $m: \mathscr{T}\to [0,\infty]$ is the measure on $(Y,\mathscr{T})$. It must satisfy: 
        \[m(X)=\mu(f^{-1}(X)),\quad \forall\, X\in\mathscr{T}. \]
        For a random variable, it is a pushforward measure(Prof. nathan talked about it in probability class). It first maps the probability space into a space, and then give it a probability measure defined by this called pushforward. 
    \end{solution}

    \begin{exercise}{5}
        A \texttt{dyadic interval} is one of the form
        \[\left(\frac{k}{2^n}, \frac{k+1}{2^n}\right], \]
        where $k, n$ are integers. Prove that every open subset of $\mathbb{R}$ is a countable disjoint union of dyadic intervals. 
    \end{exercise}

    \begin{exercise}{6}
        A measure space $(X; \mathscr{S}; \mu)$ is called complete if it contains every subset of measure $0$; that is, if $F \subset X$ and there exists a set $E \in \mathscr{S}$ with $E \subset F$ and $\mu(E) = 0$, then $F \in S$. Now suppose $(X; \mathscr{S}; \mu)$ is a measure space and let
        \[\mathscr{N}=\{N\in\mathscr{S}:\mu(N)=0\}. \]
        Define
        \[\bar{\mathscr{S}}=\{E\sup F: E\in\mathscr{S}, F\subset N for some N\subset \mathscr{N}\}. \]
        Define $\bar{\mu}: \bar{\mathscr{S}}\to[0,\infty]$ by
        \[\bar{\mu}(E\cup F)=\mu(E). \]
        Prove that $\bar{S}$ is a $\sigma$-algebra and $\bar{\mu}$ extends $\mu$ and $(\bar{\mathscr{S}}, \bar{\mu})$, is a complete measure space. 
    \end{exercise}

    \begin{exercise}{7}
        Present a discussion of \texttt{the Caratheodory procedure} to define a measure from an \texttt{outer measure}. Compare your statements from the results pre-sented in class. 
    \end{exercise}

    \begin{exercise}{8}
        Let $(X; \mathscr{A}; \mu)$ be a measure space. Assume $\mu(X) = 1$, so that this is a \texttt{probability space}. Take a collection of measurable sets fAng. Give a definition of the set of points $x \in X$ with the condition $x$ is \texttt{infinitely often} in $\{A_n\}$. Prove that this set is measurable. This is denoted by $An i.o.$ Prove that
        \[if \sum_k \mu(A_k)<\infty, \quad then \mu(A_n\ i.o.)=0. \]
        (This goes under the name \emph{the easy part of Borel-Cantelli.}) Read about the
        notion of \texttt{independence of sets} and discuss the converse of the previous
        statement.
    \end{exercise}

    \begin{exercise}{9}
        Prove \texttt{Kolmogorov 0-1 law}: if $\{A_n\}$ is a sequence of independent sets. Then
        \[
            \mu(A_n\ i.o)=\begin{cases}
                0, & \sum_{n}\mu(A_n)<\infty, \\
                1, & \sum_{n}\mu(A_n)=\infty. 
            \end{cases}
        \]
    \end{exercise}

    \begin{exercise}{10}
        Give a construction of a measure space based on the idea of flipping a coin many times. 
    \end{exercise}

    \begin{solution}
        Suppose we toss a coin $n$ times, and denote HEAD, TAIL with $0,1$. So, the sample space is $\Omega=(0,1)^n$. 

        For the $\sigma$-algebra $\mathscr{F}$, any result of tossing a coin $n$ times belongs to $\mathscr{F}$. i.e. $\mathscr{F}=2^\Omega$. 

        For the measure $P$, let 
        \[P_i(w_i=0)=p,\ p\in(0,1),\ P_i(w_i=1)=1-p\]
        \[P(\omega=(\omega_1,\omega_2,\cdots,\omega_n))=\prod_{i=1}^nP_i(\omega_i)\]
        $P(\cdot)$ is a measure of $\omega\in\Omega$, and $(\Omega, \mathscr{F}, P)$ is a measure space. Futhermore, $P(\Omega)=1$, $(\Omega, \mathscr{F}, P)$ is a probability space. 
    \end{solution}

    % \printbibliography
\end{document}
